Insert the article title here

### 2018-08-09 writeup/manuscript.tex
Tidying up methods and results draft

Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes. In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2018}. Similarly, the differences foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.

@@

@@

Sample size was determined in part by a power analysis, and in part due to constraints with counter-balancing; there are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64. $n = 64$ participants means we should be able to detect correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms. This compares to the already established value of $r \approx 0.8$ for the reliability for the ACVS paradigm.

@@

The study consists of three paradigms from the visual search literature in which large individual differences have been noted found\cite{nowakowska2017, irons-leber2016, kristjansson2014}. Example stimuli can be seen in Figure \ref{fig:exampleStimuli}. A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}.

@@

The ACVS was based on the task described in \cite{irons-leber2018}, Experiment 1.

@@

\subsection{Planned Analysis}

@@

In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}. \cite{nowakowska2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=.53$). However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$.

@@

\subsubsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowska2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with Pearson's $r \in [0.65-0.86]$ ($95\%$ confidence interval) for accuracy in finding targets on the hard heterogeneous half of the display. We get similar scores for the correlation between sessions \textit{a} and \textit{b} for heterogeneous targets, ($r \in [0.66-0.87]$), homogeneous targets ($r \in [0.56-0.82]$) and target absent ($r \in [0.65-0.86]$). The reduced correlation for the homogeneous targets is likely due to the restricted range.

@@

The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure 3?). %Figure 3 (? AC_OptCh_x_AllSw) shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$). Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber,2018}.

@@

@@

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy. As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors). Are individuals who are fast on one visual search task fast on another? In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms. While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of $r \in [0.65. 0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2016}. [AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]

@@

Mention \cite{vogel2008}.
From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual’s ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12]. Behavioral work in visual search has extended this research to
demonstrate that working memory correlates only with top-down
visual search performance where task relevance is crucial, but not
with  bottom-up  visual  search  tasks  where  salience  in  the
environment guides attention \cite{sobel2007}}

>>>>

Previous research has investigated the relationship between these behaviours to psychometric measures, but to date, these differences have not shown strong correlations with other attributes. In the ACVS paradigm, Irons \& Leber found no evidence of a correlation between the proportion of optimal choices made by observers and measures of visual working memory or trait compulsivity\cite{irons-leber2016}. Similarly, the differences foraging behaviour are not accounted for by working memory or inhibitory control\cite{johannesson2017}.

@@

The methods and planned analysis for this study were registered on the Open Science Framework\footnote{insert URL} before data collection started.

@@

Sample size was determined in part by a power analysis, and in part due to constraints with counter-balancing. $n = 64$ participants means we should be able to detect correlations with $r > 0.34$ with $\alpha = 0.05$, $\beta = 0.80$ between the different visual search paradigms. This compares to the already established value of $r \approx 0.8$ for the reliability for the ACVS paradigm.

@@

The study consists of three paradigms from the visual search literature in which large individual differences have been noted found\cite{nowakowska2017, irons-leber2016, kristjansson2014}. Example stimuli can be seen in Figure \ref{fig:exampleStimuli}. A brief overview of each paradigm is given below, with full details in \textit{supplementary materials}. The three tasks will be completed over two sessions, approximately one week apart. The split-half array search will be run in both sessions allowing us to measure test-retest reliability. The order in which participants completed the tasks was counter-balanced. There are 16 different possible orders of tasks/conditions; we will run four participants in each order for a total of 64.

@@

The ACVS was based on the task described in \cite{irons-leber2016}, Experiment 1.

@@

\subsection{Analysis Plan}

@@

Only trials with a correct target absent/present response were included in the analysis. All reaction times were $\log_2$ transformed. In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on the heterogeneous (difficult) side of the stimuli, over all correct target absent trials. Previous work\cite{nowakowska2017} demonstrated a strong correlation between this metric (for $n=5$) and reaction times ($r=.53$).

@@

\subsubsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowska2017}. Some participants performed exceptionally poorly and were removed from further analysis (full details given in the \textit{supplementary materials}).

The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with Pearson's $r \in [0.65-0.86]$ ($95\%$ confidence interval) for accuracy in finding targets on the hard heterogeneous half of the display. We get similar scores for the correlation between sessions \textit{a} and \textit{b} for heterogeneous targets, ($r \in [0.66-0.87]$), homogeneous targets ($r \in [0.56-0.82]$) and target absent ($r \in [0.65-0.86]$). The reduced correlation for the homogeneous targets is likely due to the restricted range.

@@

The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure \ref{fig:acvs_summary}). shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$). Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber2016}.

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_OptCh_x_SwRate.png}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/adaptchoice/AC_groupplot.pdf}}
\caption{Needs checked and updated. replace png with pdf!}
\label{fig:acvs_summary}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../Scripts/foraging/FG_IndivDiffsFig.png}
\caption{What do we want this figure to actually be?}
\label{fig:foraging_summary}
\end{figure}

@@

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy in each of the three paradigms. We now turn our attention to which an individual's performance in one of the tasks tells us about how well they will do in the other two. As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors). Are individuals who are fast on one visual search task fast on another? In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

The results presented above convincingly demonstrate that there are no strong correlations between the split-half, adaptive choice and foraging visual search paradigms. While we have successfully replicated the range of individual differences found in each of these studies, with a larger sample size than the original papers, the between-paradigm correlations give at most $R^2 = 0.1$, and this is a generous interpretation that would fail to pass the usual criteria for null hypothesis significance testing. Knowing how one person will behave in one of these paradigms apparently tells us very little about how they will perform in the others. This can be contrasted with the relatively high test-retest correlations of $r \in [0.65. 0.86]$ in the split-half paradigm and $r \in [0.72, 0.9]$ for the adaptive choice paradigm\cite{irons-leber2018}. [AM I RIGHT IN THINKING ARNI AND CO HAVE MEASURES FOR THEIR PARADIGM???]

@@

Mention \cite{vogel2008}.
From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual’s ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12]. Behavioural work in visual search has extended this research to
demonstrate that working memory correlates only with top-down
visual search performance where task relevance is crucial, but not
with  bottom-up  visual  search  tasks  where  salience  in  the
environment guides attention \cite{sobel2007}}
